Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-03 pecomplexity.tex
a few more tweaks

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1.0\textwidth]{figs/prediction_vs_entropy}
  \caption{The best MASE among all runs and prediction methods vs weighted
  permutation entropy. For each of these, the word length used is $6$.}
  \label{fig:pred_vs_ent}
\end{figure}

In Figures~\ref{fig:lma_pred_vs_ent} and \ref{fig:arima_pred_vs_ent} we directly
compare the performance of the LMA and ARIMA prediction methods (respectively)
to the value of the weighted permutation entropy for all runs of each program
under consideration. The LMA MASE values are largely similar to those of the
best predictions, primarily because LMA often performed superior to ARIMA and
the naive method. On the other hand, the ARIMA MASE values are largely
uncorrelated with WPE values. This however does not contradict our hypothesis,
it just means that ARIMA is ill-suited to the time series under investigation.
To see this more clearly, consider Figure~\ref{fig:lma_vs_arima}. Since larger
MASE values constitute worse predictions, ARIMA performed worse than LMA in all
traces except {\tt SVD$_1$}.

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1.0\textwidth]{figs/prediction_vs_entropy}
  \caption{The best MASE among all runs and prediction methods vs weighted
  permutation entropy. For each of these, the word length used is $6$. The
  dashed line is a least-squares linear fit of all the points except for {\tt
  SVD$_1$} which we have excluded for reasons explained in the text.}
  \label{fig:pred_vs_ent}
\end{figure}

In Figures~\ref{fig:lma_pred_vs_ent} and \ref{fig:arima_pred_vs_ent} we directly
compare the performance of the LMA and ARIMA prediction methods (respectively)
to the value of the weighted permutation entropy for all runs of each program
under consideration. The LMA MASE values are largely similar to those of the
best predictions, primarily because LMA often performed superior to ARIMA and
the naive method. On the other hand, the ARIMA MASE values are largely
uncorrelated with WPE values. This however does not contradict our hypothesis,
it just means that ARIMA is ill-suited for the time series under investigation.
To see this more clearly, consider Figure~\ref{fig:lma_vs_arima}. Since larger
MASE values constitute worse predictions, ARIMA performed worse than LMA in all
traces except {\tt SVD$_1$}.
